%------------------------
% Resume Template
% Author : Mohammad Abdullah Al Mamun
% Github : https://github.com/Mamunia
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multibib}
\usepackage{etoolbox}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
%\fancyfoot{} %when no page numbering needed
%\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large\color{black}
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Custom commands
\renewcommand{\labelitemii}{$\circ$}



%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------

\begin{center}
	\textbf{{\LARGE \color{black} Mohammad Abdullah Al Mamun}}
\end{center}
\vspace{2pt}

	\begin{minipage}{.45\linewidth} 
		\begin{flushleft}
    			Old Academic Building, Dept. of GCE \\ 
    			Bangladesh University of Engineering and Technology \\
    			Dhaka - 1000, Bangladesh; Skype: +880-1954-611668
    		\end{flushleft} 
    	\end{minipage}
    \hfill 
    \begin{minipage}{.50\linewidth}
    		\begin{flushright}
    	 		Email: \href{mailto:mamun.mme@gmail.com} {mamun.mme@gmail.com} \\
    	 		Portfolio: \href{https://mamunia.github.io/site/}{https://mamunia.github.io/site/} \\
    	 		Google Scholar: \href{https://scholar.google.com/citations?user=HzbKITAAAAAJ&hl=en}{/citations?user=HzbKITAAAAAJ$\&$hl=en} 
    		\end{flushright}
    	\end{minipage}

\vspace{5pt}
%\hrulefill


%-----------EDUCATION-----------------
\section{Education}
    \begin{minipage}{.75\linewidth} \begin{flushleft}
    		\textbf{Bangladesh University of Engineering and Technology (BUET)}
    	\end{flushleft} \end{minipage}
    \hfill 
    \begin{minipage}{.20\linewidth}\begin{flushright}
    	 Dhaka, Bangladesh
    	\end{flushright}\end{minipage}
    	
    	\begin{minipage}{.75\linewidth} \begin{flushleft}
    		M.Sc. in Glass and Ceramic Engineering;  CGPA: 3.75/4.0\\
    	\end{flushleft} \end{minipage}
    \hfill 
    \begin{minipage}{.20\linewidth}\begin{flushright}
    	 February 2020
    	\end{flushright}\end{minipage} 
	 Theis: Role of Oxygen Vacancies on Ferromagnetism in Oxide Dilute Magnetic Semiconductors: (CeO$_2$/TiO$_{2}$)\\
	
   		\begin{minipage}{.85\linewidth} \begin{flushleft}
    		B.Sc. in Materials and Metallurgical Engineering;  CGPA: 3.54/4.0 (Last 4 semesters CGPA: 3.71/4.0)\\
    	\end{flushleft} \end{minipage}
    \hfill 
    \begin{minipage}{.13\linewidth}\begin{flushright}
    	 February 2017
    	\end{flushright}\end{minipage}
	 Theis: Hydrothermal Synthesis and Characterization of Pure and Doped BiVO$_{4}$ NPs\\
	 \vspace{2pt}
	  
	  %\begin{minipage}{.75\linewidth} \begin{flushleft}
    		%\textbf{Dhaka College}
    	%\end{flushleft} \end{minipage}
    %\hfill 
   % \begin{minipage}{.20\linewidth}\begin{flushright}
    	 %Dhaka, Bangladesh
    	%\end{flushright}\end{minipage}
    	 %\vspace{2pt}
    	%\begin{minipage}{.75\linewidth} \begin{flushleft}
    		%Higher Secondary Certificate Examination;  GPA: 5.0/5.0 (Placed $23^{th}$ in Merit list)\\
    	%\end{flushleft} \end{minipage}
    %\hfill 
    %\begin{minipage}{.20\linewidth}\begin{flushright}
    	 %July 2011
    	%\end{flushright}\end{minipage}

    	%\begin{minipage}{.75\linewidth} \begin{flushleft}
    		%\textbf{Civil Aviation High School}
    	%\end{flushleft} \end{minipage}
    %\hfill 
    %\begin{minipage}{.20\linewidth}\begin{flushright}
    	 %Dhaka, Bangladesh
    	%\end{flushright}\end{minipage}
    	
    	%\begin{minipage}{.75\linewidth} \begin{flushleft}
    		%Secondary School Certificate Examination;  GPA: 5.0/5.0 (Placed $201^{th}$ in Merit list)\\
    	%\end{flushleft} \end{minipage}
    %\hfill 
    %\begin{minipage}{.20\linewidth}\begin{flushright}
    	 %May 2009
    	%\end{flushright}\end{minipage}
	 
%-----------Research Interests-----------------	    
\vspace{0pt}
\section{Research Interests}
	Emerging phenomena in 2D Materials, Complex Oxides and Organic-Inorganic Heterostructures; Advanced Spectroscopy Techniques, Synthesis, Growth $\&$ Fabrication of Flexible and Wearable Nanoelectronics Devices.\\

%-----------Awards-----------------
\vspace{0pt}
\section{Awards and Scholarships}
	\begin{description}[font=$\bullet$]
		\item{Best Oral Presentation, $2^{nd}$ Int. Conf. on Physics for Sustainable Development and Technology, 2017, Bangladesh.}
		\vspace{-5pt}
		\item {Dean's List Award, Faculty of Engineering for achieving $CGPA>3.75$ in Junior Year of B.Sc., 2016}
		\vspace{-5pt}
		\item {University Merit Scholarship for outstanding academic results in junior year of B.Sc., 2016}
		\vspace{-5pt}
		\item {$19^{th}$ at ACM – ICPC Semifinal ($9^{th}$ as ICPC Ranklist), Bangladesh Site, 2014.}
		\vspace{-5pt}
		\item {Honorable Mention, Inter University Programming Contest at Daffodil Uni., Bangladesh, 2014}
		%\vspace{-5pt}
		%\item {Government Merit Scholarship for outstanding academic results in higher secondary certificate examinations, 2012}
		
\end{description}

%-----------Publications-----------------
\vspace{-5pt}
\section{Publications}
	\nocite{*}
	\bibliographystyle{unsrt}
	\bibliography{publications}    % 'publications' is the name of a BibTeX file

%-----------Research Experience-----------------
\vspace{-5pt}
\section{Research Experience}
	\begin{description}[font=$\bullet$]
		\item{Hands on experience in synthesis of multifunctional nanoparticles ($TiO_{2}$, $CeO_{2}$, $BiFeO_{3}$, $BiVO_{4}$) using solid state and different wet chemical routes such as sol-gel, hydrothermal, co-precipitation etc.}
		\vspace{-5pt}
		\item{Hands on experience in thin film deposition using spin coater ($TiO_{2}$ and $CeO_{2}$) and thermal evaporator (ZnSe).}
		\vspace{-5pt}
		\item{Material Characterization Analysis: X-Ray Diffraction (XRD), Scanning Electron Microscopy (SEM), Transmission Electron Microscopy (TEM), Selective Area Electron Diffraction (SAED), UV-Visible and Photoluminescence Spectroscopy, X-Ray Photoelectron Spectroscopy (XPS).}
		\vspace{-5pt}
		\item{Electrical and Magnetic Characterization Analysis: Dielectric Properties such as resistance, reactance, AC conductivity, AC resistivity; Ferroelectric Properties (P-E hysteresis); Magnetic Properties (M-H hysteresis).}
		\vspace{-5pt}
		
	\end{description}
	
%-----------Technical Skills-----------------
\vspace{-5pt}
\section{Technical Skills}
	Programming: C, C++, Python, \LaTeX; Scientific Computing Environment: MATLAB, Originpro.\\ 
	

\end{document}



